Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models

### 2024-03-14 paper_version/main.tex
Add files via upload

\newcommand{\mycolorbox}[2]{\colorbox{#1}{$\displaystyle#2$}}
\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
\newcommand{\mycomment}[1]{\noindent\textcolor{orange}{\underline{\textsf{\textbf{#1}}}}}
\newcommand{\todobox}[1]{
    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
        #1
    \end{tcolorbox}
}

@@

\newcommand{\review}[1]{\textcolor{blue}{\if\ifUpdate1\textbf{#1}\fi}}

\title{Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models}
\author[]{Tianwei Yu \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{tianwei.yu@math.ethz.ch}}}
\author[]{Roman Fuchs \thanks{IET Institut für Energietechnik, OST, \texttt{roman.fuchs@ost.ch}}}
\author[]{Ralf Hiptmair \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{ralf.hiptmair@math.ethz.ch}}}
\affil[]{}
\date{}

@@

@@

%An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
%}

@@

% \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
The starting point for this work was the desire to numerically simulate the formation and
evolution of electric arcs at atmospheric pressures. Following common practise, we rely on
a mathematical description by means of a hydrodynamic multi-species plasma model, which
boils down to an extended Maxwell-Euler system. The arc phenomenon covers a wide range of
plasma regimes and, thus, the design goal was a numerical model capable of dealing
with all of them seamlessly and simultaneously. Thus in this work, as in
\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
length, see Section~\ref{sec:rescaling} for the underlying scaling arguments and
\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
numerical plasma models.

Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
\begin{itemize}
\item We supplement the Maxwell-Euler system by inter-species friction terms.
\item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three
  spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's
  equations combined with a low-order finite volume method for Euler's equations.
\item We propose a stabilization in non-conducting regions which is essential for the
  efficacy of our method.
\end{itemize}

We stay close to \cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping. We base our illustration on the model case shown
in Fig.~\ref{fig:domain_geometry}. Yet we would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to geometric situations much
more general than that of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not 
assume the problem to enjoy the rotational symmetry. If the symmetry is assumed, 
it can be exploited for reduction to two spatial dimensions \cite{bonotto_2022}.}

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes. 
Beside the quasi-neutral limit, we remind
that singularly perturbed problems occur in extensively many physical models, 
e.g., in the case of vanishing viscosity problem \cite{Kato_1984, bianchini_2005, temam_1997}, the
zero-relaxation-limit of kinetic-type equations \cite{raymond_2009, degond_1996}, and the incompressible limit
of compressible flows \cite{klainerman_1981}. Throughout, it is essential that
numerical schemes remain valid even if crucial model parameters approach the limit. These
schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
discretization parameter, e.g., the mesh size. The AP property amounts to uniform
convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. 
The concept is effectively depicted by a commuting diagram in \cite[][Fig.~1]{jin_2010}. 
\review{AP schemes have been extensively studied for various problems, e.g. the diffusive limit of the kinetic equations \cite{jin_1999, liu_2023}, 
the low Mach-number limit of compressible flows \cite{degond_2007, haack_2010} and magnetohydrodynamics\cite{chen_2023}, 
the quasi-neutral limit of drift-diffusion equations \cite{chatard_2014, claire_2007}. 
More generally, readers are referred to the comprehensive reviews \cite{jin_2010, degond_2017}.}

The content of this paper is organized as follows: In Section~\ref{sec:plasma-model}, we
give a full description of the underlying equations of the Maxwell-Euler system and its
rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
reformulation of Maxwell's equations in the non-conducting region is presented. Section
\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
full AP discretization in Section~\ref{sec:full-discretization} and do numerical
experiments in Section~\ref{sec:numerical_experiment}.

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=1.2]
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[violet] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
    \caption{The special geometric setting suggested by the simulation of electric arcs,
      for which we discuss the new method.}
\label{fig:domain_geometry}
\end{figure}

\section{Plasma model} \label{sec:plasma-model}

@@

Plasmas consist of electrically charged and (possibly) neutral particle species and we
suppose that they can be treated as continua (fluids). That is, they may be described by the
Navier-Stokes equations augmented with source terms for species generation (ionization,
recombination), forces (Lorentz force and interspecies friction), and energy (thermal
relaxation among species, radiative heat transfer, Ohmic heating). For more details on
fluid models of plasmas, see \cite{chen2016, remi_2014}.

@@

We model each species in the plasma as a compressible fluid through a set of \emph{Euler
  equations} augmented by electromagnetic forces as well as other processes,
e.g. collisions and recombination:
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species. The
involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass
$m_*[\text{kg}]$, electric charge $q_*[\text{C}]$, velocity
$\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$,
specific total energy
$e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma -
  1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy
$h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density
$\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All species are
assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The
left-hand side of the equations describes the convection of plasma fluids. The first term
at the right-hand side takes into account the Lorentz force in the momentum equation and
Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due
to effects of inter-species collision, ionization, recombination, etc.

@@

\begin{remark}
  \label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance \citep[][Sec.~5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g. ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
\cite[][Sec.~3.2]{fuchs_2021}.
\end{remark}

\subsection{Rescaling}
\label{sec:rescaling}
% In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite[][Sec.~2.2]{degond_2017}.

We arrive at non-dimensional equations by following the rescaling procedure of
\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

@@

Assumptions can be made to reduce the number of dimensionless parameters. Following
\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order
one and $\xi$ has the same magnitude as $\lambda$.

>>>>

\newcommand{\mycolorbox}[2]{\colorbox{#1}{$\displaystyle#2$}}
\newcommand{\todo}[1]{\textcolor{green!50!black}{\fbox{\textbf{TODO: #1}}}}
\newcommand{\mycomment}[1]{\noindent\textcolor{orange}{\underline{\textsf{\textbf{#1}}}}}
\newcommand{\todobox}[1]{
    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
        #1
    \end{tcolorbox}
}

@@

\newcommand{\review}[1]{{\color{blue}{\if\ifUpdate1\sf{#1}\fi}}}

\title{Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models}
\author[]{Tianwei Yu \thanks{Seminar for Applied Mathematics, ETH Z\"{u}rich, \texttt{tianwei.yu@math.ethz.ch}}}
\author[]{Roman Fuchs \thanks{IET Institut für Energietechnik, OST, \texttt{roman.fuchs@ost.ch}}}
\author[]{Ralf Hiptmair \thanks{Seminar for Applied Mathematics, ETH Z\"{u}rich, \texttt{ralf.hiptmair@math.ethz.ch}}}
\affil[]{}
\date{(1)}

@@

% \todo{Do not directly insert numbers of formulas, figure, sections. Always use \LaTeX's
%  \symbol{92}label-\symbol{92}ref facility.}

@@

%An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by~\cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
%}

@@

% \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
The starting point for this work was the desire to numerically simulate the formation and
evolution of electric arcs at atmospheric pressures. Following common practise, we rely on
a mathematical description by means of a hydrodynamic multi-species plasma model, which
boils down to an extended Maxwell-Euler system. The arc phenomenon covers a wide range of
plasma regimes and, thus, the design goal was a numerical model capable of dealing
with all of them seamlessly and simultaneously. Thus, in this work, as in
~\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
length, see Sec.~\ref{sec:rescaling} for the underlying scaling arguments and
~\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
numerical plasma models.

Our approach is inspired by~\cite{degond_2012}, but goes beyond that work in various directions:
\begin{itemize}
\item We supplement the Maxwell-Euler system by inter-species friction terms.
\item We extend the spatially one-dimensional scheme of~\cite{degond_2012} to three
  spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's
  equations combined with a low-order finite volume method for Euler's equations.
\item We propose a stabilization in non-conducting regions which is essential for the
  efficacy of our method.
\end{itemize}

We stay close to~\cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping and base our illustration on the model situations shown in
Fig.~\ref{fig:domain_geometry}. Yet, we would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to settings more general
than those of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not assume any
  rotational symmetry, which would allow reduction to two spatial dimensions~\cite{bonotto_2022}.}

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes.  Beside the
quasi-neutral limit, we remind that singularly perturbed problems occur in extensively
many physical models, e.g., in the case of vanishing viscosity problem~\cite{Kato_1984,
  bianchini_2005, temam_1997}, the zero-relaxation-limit of kinetic-type equations
~\cite{raymond_2009, degond_1996}, and the incompressible limit of compressible flows
~\cite{klainerman_1981}. Throughout, it is essential that numerical schemes remain valid
even if crucial model parameters approach the limit. These schemes are then said to be
\emph{asymptotic-preserving} (AP): Let us assume that we discretize a
parameter (denoted by $\lambda$) dependent model $P^\lambda$, which converges to a limit $P^0$ as
$\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization
parameter, e.g., the mesh size. The AP property amounts to uniform convergence of
$P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.  The concept is effectively
depicted by a commuting diagram in~\cite[][Fig.~1]{jin_2010}.  \review{AP schemes have
  been extensively studied for various problems, e.g., the diffusive limit of kinetic
  equations~\cite{jin_1999, liu_2023}, the low Mach-number limit of compressible flow
  models~\cite{degond_2007, haack_2010}, magnetohydrodynamics~\cite{chen_2023}, the
  quasi-neutral limit of drift-diffusion equations~\cite{chatard_2014, claire_2007}.  For
  more information readers are referred to the comprehensive reviews~\cite{jin_2010,
    degond_2017}.}

The content of this paper is organized as follows: In Sec.~\ref{sec:plasma-model}, we
give a full description of the underlying equations of the Maxwell-Euler system and its
rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
reformulation of Maxwell's equations in the non-conducting region is presented. Sec.
~\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
full AP discretization in Sec.~\ref{sec:full-discretization} and do numerical
experiments in Sec.~\ref{sec:numerical_experiment}.

\begin{figure}
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.9]
        \coordinate (O1) at (0,0);
        \draw[violet] (O1) circle (1) node[blue] {Electrode};
        \fill[blue, opacity=0.2] (O1) circle (1);
        \draw[very thick] (O1) circle (1.5);
        \coordinate (O2) at (4.5,1);
        \draw[violet] (O2) circle (1);
        \node at (O2) {\textcolor{red}{Electrode}};
        \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
        \fill[red, opacity=0.2] (O2) circle (1);
        \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
        \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
        \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
        \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
        \draw[violet] (S1) -- (S2);
        \draw[violet] (P1) -- (P2);
        \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
        \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
        \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
        \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
        \draw[very thick] (SS1) -- (SS2);
        \draw[very thick] (PP1) -- (PP2); 
        \draw[violet] (SS2) arc (101.31:180+101.31:1.5);
        \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
        \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
        \end{tikzpicture}
        \caption{Cylinder geometry}\label{fig:cylinder_geo}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            % Electrode 1
            \coordinate (O1) at (0,0);
            \draw[violet] (O1) rectangle ++(2,2) node[midway, blue] {Electrode};
            \fill[blue, opacity=0.2] (O1) rectangle ++(2,2);

            % Electrode 2
            \coordinate (O2) at (4.5,1);
            \draw[violet] (O2) rectangle ++(2,2) node[midway, red] {Electrode};
            \fill[blue, opacity=0.2] (O2) rectangle ++(2,2);

            \coordinate (_O1) at (-0.5, -0.5);
            \coordinate (_O2) at (4.0,0.5);
            \draw[very thick] (_O1) rectangle ++(3,3);
            \draw[very thick] ([shift={(3,0)}]_O2) -- ++(0,3) -- ++(-3,0);
            \draw[violet] (_O2) -- ++(3,0);
            \draw[violet] (_O2) -- ++(0,3); 
            \coordinate (_N1) at  ([shift={(0,3)}]_O1);
            \coordinate (_E1) at  ([shift={(3,0)}]_O1);
            \coordinate (_NE1) at ([shift={(3,3)}]_O1);
            \coordinate (_N2) at  ([shift={(0,3)}]_O2); 
            \coordinate (_E2) at  ([shift={(3,0)}]_O2);
            \coordinate (_NE2) at ([shift={(3,3)}]_O2); 
            \draw[violet] (_O1) -- (_O2);
            \draw[very thick] (_N1) -- (_N2);
            \draw[very thick] (_E1) -- (_E2);
            \draw[very thick] (_NE1) -- (_NE2);

            \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
        \end{tikzpicture}
        \caption{Cuboid geometry}\label{fig:cube_geo}
    \end{subfigure}
    \caption{The special geometric setting suggested by the simulation of electric arcs,
        for which we discuss the new method.
        % \todo{Move geometry from Fig.~9 here. Display both side-by-side.}
    }
    \label{fig:domain_geometry}
\end{figure}

\section{Plasma model}\label{sec:plasma-model}

@@

Plasmas consist of electrically charged and (possibly) neutral particle species, and we
suppose that they can be treated as continua (fluids). That is, they may be described by the
Navier-Stokes equations augmented with source terms for species generation (ionization,
recombination), forces (Lorentz force and interspecies friction), and energy (thermal
relaxation among species, radiative heat transfer, Ohmic heating). For more details on
fluid models of plasmas, see~\cite{chen2016, remi_2014}.

@@

We model each species in the plasma as a compressible fluid through a set of \emph{Euler
  equations} augmented by electromagnetic forces as well as other processes,
e.g.\ collisions and recombination:
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \ldots\}$ labels electrons, ions or other species. The
involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass
$m_*[\text{kg}]$, electric charge $q_*[\text{C}]$, velocity
$\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$,
specific total energy
$e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma -
  1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy
$h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density
$\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All species are
assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The
left-hand side of the equations describes the convection of plasma fluids. The first term
at the right-hand side takes into account the Lorentz force in the momentum equation and
Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due
to effects of inter-species collision, ionization, recombination, etc.

@@

\begin{remark}\label{rem:coll}
  For the sake of simplicity, we only consider ion-electron collision in this work, but
extension to more species is straightforward. Such collisions can be well modelled by
friction terms, for instance~\citep[][Sec.~5.6.2]{chen2016}
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{{(4\pi\epsilon)}^2{(k_B T_e)}^{3/2}}\text{\emph{ln}}\Lambda n_e n_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
  logarithm} and is usually taken as a constant~\cite{chen2016}. Because of the
conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
effects, e.g.\ ionization and recombination, are not considered. For full details about the
modeling of these physical processes, readers are referred to
~\cite[][Sec.~3.2]{fuchs_2021}.
\end{remark}

\subsection{Rescaling}\label{sec:rescaling}
% In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of~\cite[][Sec.~2.2]{degond_2017}.

We arrive at non-dimensional equations by following the rescaling procedure of
~\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
interest, by which the reference velocity $\overline{v}$ is defined as
$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
reference value for the specific total energy and enthalpy is set to
$\overline{u}^2$. Also taking into account the physical constants, i.e.\ the reference
permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
speed $c^2 = {(\overline{\epsilon}\overline{\mu})}^{-1}$, Boltzmann constant $k_B$, the
elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
parameters:
\begin{align*} 
  \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
  \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
  M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
  \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
  \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
  \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\ldots\}, &\\
  g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see~\cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

@@

Assumptions can be made to reduce the number of dimensionless parameters. Following
~\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order
one and $\xi$ has the same magnitude as $\lambda$.

\begin{remark}
Special treatment is needed for the collision term. One could argue that the occurrence of
$\lambda^{-1}$ in (\ref{equ:rescaling_friction}) could lead to singular perturbation of
the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision
model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding
effect characterized by the rescaled Debye length $\lambda$ limits the impact parameters
to values $\sim\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions
happen on the atomic length scale, in which quantum-mechanical effects must be taken into
account~\cite[][pp. 144-148]{frank_1972}. Therefore, we eliminate the perturbation
parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor
$\alpha^{\text{coll}}$ of the collision term constant throughout the simulation.

The case when there is an asymptotic parameter in the denominator of the friction term is
of interest, too. This situation is known as relaxation limit, see~\cite{peng_2011,
  wasiolek_2016, Li_2021, Chen_2000}.
\end{remark}
